Continuations via Negative Information Flow

### 2012-02-15 dual.tex
intro

We introduced this thesis that computation should be based on isomorphisms
that preserve information~\cite{infeffects}.

@@

>>>>

We introduced this thesis that computation should be based on isomorphisms
that preserve information~\cite{infeffects}. Since Filinski, we've had the
idea that values and continuations are like mirror images. In a conventional
language, the negative (continuation) side is implicit and we introduce
information effects on the positive. Trying to recover the duality from this
distorted positive side has always been messy. Now it looks clean because we
have kept the positive side pure.

The way to think about something of type $A$ is that it is a value we have
produced. The way to think about something of type $-A$ is that is a value we
have already consumed.

Other interpretations of the types of think about. The first one is
arithmetic obviously. Another one is languages consisting of sets of
string. The type 0 is the empty set, the type 1 is the set containing the
empty word, the $+$ constructor corresponds to union, and the $*$ constructor
corresponds to concatenation. The constructor $-$ would not correspond to set
difference however. It would correspond to marking the elements in the set as
``consumed'' so that if we take the union and a ``consumed'' element appears
in the other set, the two cancel. This makes it clear that concatenating a
produced $a$ and a consumed $b$ is not the same as concatenating a consumed
$a$ and a produced $b$. They really need to be kept separate. Incidentally,
division would be defined as follows:
\[
L_1 / L_2 = \{ x ~|~ xy \in L_1 \mbox{~for~some~} y \in L_2 \}
\]

@@

Lifting a operation of postive types to negated types:

Given {{c : b1 <-> b2}}

\begin{center}
  \includegraphics{diagrams/neg_lift.pdf}
\end{center}
